### 2011-05-12 paper/paper.tex
fixed a bunch of typos from our feedback

Here, we study two Markov chain-based methods for sampling, the \emph{Metropolis} method \cite{Metropolis}, and the \emph{hit-and-run} \cite{Vempala} method, and we see how they perform comparatively in practice. The Metropolis method is the simpler of the two. We walk around the region in the following way: from a point $x$, we choose another random point in a ball around that point from some distribution. If this new point lies in the convex region, then we jump to it; otherwise, we stay at $x$. We get a Markov chain $x_0, x_1, ...$, and after sufficiently many iterations, we take the point we are at to be our random point.

>>>>

Here, we study two Markov chain-based methods for sampling, the \emph{Metropolis} method \cite{Metropolis}, and the \emph{hit-and-run} \cite{Vempala} method, and we see how they perform comparatively in practice. The Metropolis method is the simpler of the two. We start at some point and randomly walk around the region in the following way: from a point $x$, we choose another random point from some distribution based off of that point. If this new point lies in the convex region, then we jump to it; otherwise, we stay at $x$. We get a Markov chain $x_0, x_1, ...$, and after sufficiently many iterations, we take the point we are at to be our random point.
